Wilcoxon results tables - text and appendix

### 2017-12-08 analyses/06-table-wilcox.Rmd
finish wilcox tables code

---
title: "Wilcoxon results tables"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

# Extract epoch only, and proximity and gradual split models
# Remove excess columns
# Add model column name
fix.wilcox <- function(data){
  data %>%
  filter(V5 == "Epoch") %>%
  select(-c(V1,V2, V5)) %>%
  filter(V3 == "proximity" | V3 == "gradual.split") %>%
  spread(V4, V6) %>%
  rename(model = V3)
}

wilk2 <- purrr::map(wilk, p.values.function)
wilk3 <- purrr::map_df(wilk2, fix.wilcox)
wilk3$dataset <- c(rep(unlist(slugs)[1], 2), rep(unlist(slugs)[2], 2), 
                   rep(unlist(slugs)[3], 2), rep(unlist(slugs)[4], 2))

@@

## Create table for epochs

```{r}
## variable names
colnames <- c("Dataset", "Model", "Stratigraphy", "Duration", "Number")

## Formatting the table
table_out <- data.frame(wilk3$dataset, wilk3$model, wilk3$stratigraphy,
                        wilk3$duration, wilk3$number)
colnames(table_out) <- colnames

@@

sink(file = "../manuscript/tables/raw_wilcox_epoch.tex")
print(xtable(table_out, caption = table_caption), include.rownames = FALSE)
sink()
```

## Repeat for appendix tables with epoch and age and all models

@@

wilk2 <- purrr::map(wilk, p.values.function)
wilk3 <- purrr::map_df(wilk2, fix.wilcox.appendix)
wilk3$dataset <- c(rep(unlist(slugs)[1], 2), rep(unlist(slugs)[2], 2), 
                   rep(unlist(slugs)[3], 2), rep(unlist(slugs)[4], 2))

>>>>

---
title: "Wilcoxon results tables - text and appendix"
author: "Natalie Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_width: 12
    fig_height: 12
---

@@

# Extract proximity and gradual split models
# Remove excess columns
# Add model column name
fix.wilcox <- function(data){
  data %>%
  select(-c(V1,V2)) %>%
  filter(V3 == "proximity" | V3 == "gradual.split") %>%
  spread(V4, V6) %>%
  arrange(V5) %>%
  rename(model = V3) %>%
  rename(period = V5)  
}

wilk2 <- purrr::map(wilk, p.values.function)
wilk3 <- purrr::map_df(wilk2, fix.wilcox)
wilk3$dataset <- c(rep(unlist(slugs)[1], 4), rep(unlist(slugs)[2], 4), 
                   rep(unlist(slugs)[3], 4), rep(unlist(slugs)[4], 4))

@@

## Create table

@@

sink(file = "../manuscript/tables/raw_wilcox.tex")
print(xtable(table_out, caption = table_caption), include.rownames = FALSE)
sink()
```

## Repeat for appendix tables with all models

@@

wilk2 <- purrr::map(wilk, p.values.function)
wilk3 <- purrr::map_df(wilk2, fix.wilcox.appendix)
wilk3$dataset <- c(rep(unlist(slugs)[1], 12), rep(unlist(slugs)[2], 12), 
                   rep(unlist(slugs)[3], 12), rep(unlist(slugs)[4], 12))
